---
output:
  html_document: default
  pdf_document: default
---
# Scopus Search Scrape
The code below makes scrapes search data from Scopus to collate the count of published documents from specific search terms.

```{r}
library(rvest)
library(stringr)
library(reshape)
library(readr)
library(gplots)
library(ggplot2)
library(viridis)
library(scico)
library(RColorBrewer)
```

First, get a general search URL from Scopus. Here, I have generally just searched for $urbanisation$. 

```{r}
URL <-'https://www.scopus.com/results/results.uri?numberOfFields=0&src=s&clickedLink=&edit=&editSaveSearch=&origin=searchbasic&authorTab=&affiliationTab=&advancedTab=&scint=1&menu=search&tablin=&searchterm1=urbanisation&field1=TITLE_ABS_KEY&dateType=Publication_Date_Type&yearFrom=Before+1960&yearTo=Present&loadDate=7&documenttype=All&accessTypes=All&resetFormLink=&st1=urbanisation&st2=&sot=b&sdt=b&sl=27&s=TITLE-ABS-KEY%28urbanisation%29&sid=86370a09dc97d6df569d5e77acaf3d6e&searchId=86370a09dc97d6df569d5e77acaf3d6e&txGid=40c0feb404cc754db4a2c091d1aacd07&sort=plf-f&originationType=b&rr='
```

We then get a list of search terms. Here it is a $.csv$ of urbanisation themes work in Southeast Asia. Note the syntax for searching in the CSV. 
```{r}
theme <- read.csv("names.csv", header = FALSE)
theme <- unlist(lapply(function(X) paste("", theme$V1[X], "", sep = ""), X = 1:length(theme$V1)))

head(theme)
```

Going through the list of these themes - for example $Southeast_Asia+Accessibility$, we create a list of URLs that R will go through. It subs our general $urbanisation$ term out with the search terms listed in the $names.csv$. 

The function to run through all the hyperlinks created in our $URLS$ item. $.resultsCount$ is the element name within the Scopus search results page. 

```{r}
URLS <- lapply(function(X) gsub("urbanisation", theme[X], URL), X = 1:length(theme))

themecounts <- rep(NA, length(theme))

for(i in 1:length(URLS))
{
  # print(i/length(URLS))
  readingSite <- read_html(URLS[[i]]) # read the html from site 
  numberOfHits <- as.character(html_nodes(readingSite, ".resultsCount")) # extract specific info
  if(length(numberOfHits) == 0)
  {
  themecounts[i] <- 0
  print("none") 
  next()  
  }
  print(numberOfHits) # print number of hits
  themecounts[i] <- str_extract_all(numberOfHits,"\\(?[0-9,.]+\\)?")[[1]]
}
``` 

Combining theme names with counts
```{r}
fullData <- data.frame(theme = theme, counts = unlist(themecounts))
head(fullData)

write.csv(fullData, file = "ScopusSearch.csv", row.names = FALSE)

data <- read.csv("ScopusSearch.csv")

```

# Creating a heatmap for our results.

I cleaned the data in Excel and imported with the $count$ set to numeric. You can do it in R.
```{r}
data_cleaned <- read_csv("data_cleaned.csv", 
    col_types = cols(Accessibility = col_number(), 
                     Equity = col_number(),
                     `Land Cover` = col_number(), 
                     `Land use` = col_number(),
                     Mobility = col_number(),
                    Segregation = col_number(), 
                    `Spatial Interaction` = col_number(), 
                    Sprawl = col_number(), 
                    `Urban Accessibility` = col_number(), 
                    `Urban Development` = col_number(),
                    `Urban Growth` = col_number(),
                    `Urban Segregation` = col_number(),
                    Urbanisation = col_number()))
str(data_cleaned)
data.1 <- as.data.frame(data_cleaned)
```


Preparing the data as matrix
```{r}
row.names(data.1) <- data_cleaned$region
data <- data.1[,2:14]
data.m <- data.matrix(data)
ScopusSearch_2 <- melt(data.m)
```

Heatmap with base R
```{r}
heatmap <- heatmap.2(data.m, 
                     trace = 'none',
                     scale='none', 
                     col=brewer.pal(11, 'RdBu'))

heatmap2 <- heatmap.2(data.m, 
                      scale = "none", 
                      col = bluered(100), 
                      trace = "none", 
                      density.info = "none")

data.2 <- as.data.frame(ScopusSearch_2)

``` 

```{r}
hm.palette <- colorRampPalette(rev(brewer.pal(9, 'PuBuGn')), space='Lab')

ggplot(data.2, aes(data.2$X2,X1, fill=value)) +
  geom_tile() +
  scale_x_discrete() +
  scale_y_discrete() +
  scale_fill_viridis()+
  geom_text(aes(label = round(value))) +
  theme_minimal()
  
```

```{r}
yes_map <- heatmap.2(data.m,
                     cellnote = data.m,
                     notecex = 1,
                     Rowv = NA,
                     Colv=NA,
                     sepcolor = 'white',
                     sepwidth = c(0.05,0.05),
                     notecol = 'White',
                     scale ='none',
                     density.info ='none',
                     trace='none',
                     dendrogram = 'none',
                     na.color=par("bg"),
                     col=viridis(1000),
                     key=TRUE)
```


